\\documentclass[conference]{IEEEtran}
\usepackage[backend=biber]{biblatex} 
\addbibresource{references.bib}
\title{%
 Medml lab 3 \\
  \large X-ray

\author{Pham Dinh Bao Khoi - 23BI14230}

\begin{document}

\maketitle
\section{Introduction}


\section{related works}


\section{Experimental}
\subsection{setup}
all experimental is done on Kaggle notebook with GPU P100
\subsection{EDA datset}
\subsection{modeling}


\section{result}


\section{Reference}
    \item https://www.kaggle.com/code/rohnkr/resunet
    
   \item Sanida, T., Tabakis, I.-M., Sanida, M. V., Sideris, A., & Dasygenis, M. (2023). A Robust Hybrid Deep Convolutional Neural Network for COVID-19 Disease Identification from Chest X-ray Images. Information, 14(6), 310. https://doi.org/10.3390/info14060310
   \item Aadesh Taneja. Enhancing COVID-19 Classification in Chest X-ray Images through CNN-based Model Optimization Techniques, 28 November 2024, PREPRINT (Version 1) available at Research Square [https://doi.org/10.21203/rs.3.rs-5404776/v1]
   \item Kuzinkovas, D., & Clement, S. (2023). The Detection of COVID-19 in Chest X-rays Using Ensemble CNN Techniques. Information, 14(7), 370. https://doi.org/10.3390/info14070370
   \item Constantinou, M., Exarchos, T., Vrahatis, A. G., & Vlamos, P. (2023). COVID-19 Classification on Chest X-ray Images Using Deep Learning Methods. International Journal of Environmental Research and Public Health, 20(3), 2035. https://doi.org/10.3390/ijerph20032035
   \item Ibrokhimov, B., & Kang, J.-Y. (2022). Deep Learning Model for COVID-19-Infected Pneumonia Diagnosis Using Chest Radiography Images. BioMedInformatics, 2(4), 654-670. https://doi.org/10.3390/biomedinformatics2040043



\end{document}

